\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-03-19 manuscript/manuscript.tex
comments on intro

\jy{Start from the need for KS test for stationary series; review existing works
  and identify the gap; summarize the contribution.}

The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. 
Let $X_1, ..., X_n$ be a random sample of size~$n$ from some continuous
distribution and the null hypothesis $H_0$ be that $X_i$'s follow the
hypothesized distribution~$F$.
If we let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function, the KS test statistic takes the form
\begin{equation}
  \label{eq:ks_standard}
  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
\end{equation}
As sample size $n\to \infty$, the distribution of $T_n$ converges to that of the
absolute value of standard Brownian bridge, which is known as the Kolmogorov
distribution \citep{stephens1974edf}. The distribution function can be
accurately evaluated in modern statistical software
\citep{marsaglia2003evaluating}. The KS test can be applied to a variety of
fields. \jy{cite a few  references in various field to show its wide
  applications.}
 It has
been used to analyze the random distribution of cosmic microwave background 
radiation \citep{naess2012application}. \citep{aslam2020introducing} 
applied the method to test if the count rate per second of
radioactive data followed the Poisson distribution. 
Researchers have proposed the
method as a technique for gear condition monitoring \citep{andrade2001gear}. It
can also be used to compare images of breast
cancer tumors \citep{demidenko2004kolmogorov}.

Despite its widespread use, the KS test can be 
misapplied when its foundational assumptions are overlooked. The KS test 
assumes the data are independently and identically distributed (i.i.d.) and 
that the hypothesized distribution is continuous and fully specified without 
the need for parameter estimation. \citet{zeimbekakis2022misuses} examines 
common misapplications of the one-sample KS test, notably the inappropriate
use when the hypothesized distribution contains unspecified parameters.
For this situation, \citet{zeimbekakis2022misuses} proposed a parametric
bootstrap, where bootstrap samples of the test statistics are constructed from samples generated from the fitted hypothesized distribution.
Alternatively, \citet{babu2004goodness} addresses this issue through the
application of basic non-parametric bootstrap methods.
Another commonly encountered situation is when the data are serially
dependent.
\citet{zeimbekakis2022misuses} proposed a semi-parametric bootstrap
where the serial dependence structure is modeled via a working serial copula.
A particularly complex scenario arises when the distribution has unspecified
parameters, and the data are serially dependent. For this,
\citet{zeimbekakis2022misuses} also recommends a semi-parametric bootstrap
approach, where the parameters of the hypothesized distribution and the serial
dependence both need to be estimated and their uncertainty accounted for.

>>>>

The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. 
Let $X_1, ..., X_n$ be a random sample of size~$n$ from some continuous
distribution and the null hypothesis $H_0$ be that $X_i$'s follow the
hypothesized distribution~$F$.
If we let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function, the KS test statistic takes the form
\begin{equation}
  \label{eq:ks_standard}
  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
\end{equation}
As sample size $n\to \infty$, the distribution of $T_n$ converges to that of the
absolute value of standard Brownian bridge, which is known as the Kolmogorov
distribution \citep{stephens1974edf}. The distribution function can be
accurately evaluated in modern statistical software
\citep{marsaglia2003evaluating}. The KS test can be applied to a variety of
fields. Examples are cosmic microwave background 
radiation \citep{naess2012application},
count rate of redioactive data??? \citep{aslam2020introducing},
gear condition monitoring \citep{andrade2001gear}, and
images of breast cancer tumors \citep{demidenko2004kolmogorov}.

Despite its widespread use, the KS test can be 
misapplied when its foundational assumptions are overlooked. The KS test 
assumes the data are independently and identically distributed (i.i.d.) and 
that the hypothesized distribution is continuous and fully specified without 
the need for parameter estimation. \citet{zeimbekakis2022misuses} examines 
common misapplications of the one-sample KS test, notably the inappropriate
use when the hypothesized distribution contains unspecified parameters.
For this situation, \citet{zeimbekakis2022misuses} proposed a parametric
bootstrap, where bootstrap samples of the test statistics are constructed from
samples generated from the fitted hypothesized distribution.
Alternatively, \citet{babu2004goodness} addresses this issue through the
application of basic non-parametric bootstrap methods.
Another commonly encountered situation is when the data are serially
dependent.
\citet{zeimbekakis2022misuses} proposed a semi-parametric bootstrap
where the serial dependence structure is modeled via a working serial copula.
A particularly complex scenario arises when the distribution has unspecified
parameters, and the data are serially dependent. For this,
\citet{zeimbekakis2022misuses} also recommends a semi-parametric bootstrap
approach, where the parameters of the hypothesized distribution and the serial
dependence both need to be estimated and their uncertainty accounted for.
\jy{This reference is an example of abuse in time series settings:
Tuncer, O., Ates, E., Zhang, Y., Turk, A., Brandt, J., Leung, V. J., Egele, M., and Coskun, A. K. (2019), “Online Diagnosis of Performance Variation in HPC Systems Using Machine Learning,” IEEE Transactions on Parallel and Distributed Systems, 30, 883–896.
}
